Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 experiments.tex
started pass over ex

%
In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a

Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors. This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.

\subsection{2D-3D Matching as an Object Detector}

We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}. MPPE is the average of viewpoint accuracy.

% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}

Our ensemble of NZ-WHO templates is generated from rendering images within few minutes but shows reasonable performance on object detection task. The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.

The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.

\begin{table}[!htbp]
    \footnotesize
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category. Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
  \label{tab:3dobject}
\end{table}

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
  \label{fig:3dobject}
\end{figure}

@@

\subsection{Fine-Tuning and Viewpoint Estimation}

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

>>>>

%
In this section, we give an experimental evaluation of our approach,
highlighting two different aspects.

First, we demonstrate that our method can be used for multi-view
object class detection in isolation. It can be applied in a sliding
window fashion and deliver 2D bounding box as well as viewpoint
information. Our method compares on par to state-of-the-art in this
case (Sect.~\ref{sec:exp_iso}).

Second, we show that our method can be used to complement the
detections provided by an existing object class detector, such
as DPM~\cite{Felzenszwalb10} or RCNN~\cite{Girshick14}. In this case,
we show a considerable performance improvement compared to previous
work in the task of joint object class detection and viewpoint
estimation (Sect.~\ref{sec:exp_enrich}).

\paragraph{Setup.}
We use established benchmark datasets to validate our approach, namely
the 3D Object Classes dataset~\cite{Savarese07}, and
PASCAL3D+~\cite{Xiang14}, a recently proposed extension of Pascal
VOC'12~\cite{pascal12} that provides additional annotations in the
form of aligned 3D CAD models. In both cases, we use the test data
provided by the respective datasets, but train our models entirely
from rendered 3D CAD model images.

% In this section, we validate our proposed NZ-WHO templates in two
% different ways. First, we make a set of NZ-WHO templates for a set of
% CAD models from various viewpoints. Then we run the bank of NZ-WHO
% templates as ensembles of weak detectors and show that the rendering
% image can be We want to see how robust the NZ-WHO to real images a
%
% Second, we show that our method can complement the detection bounding
% boxes coming out of standard object detectors. This process will
% enrich object detection bounding boxes with 2D-3D matching which gives
% continuous viewpoint estimation, a CAD model (rendering, depth) and
% fine-grained category.

\subsection{2D-3D Matching as an Object Detector} 
\label{sec:exp_iso}
In this section, we evaluate the performance of our method in
isolation, for the task of object class detection and viewpoint
estimation, on the 3D Object Classes datset~\cite{Savarese07}, for the
categories {\em car} and {\em bicycle}.

To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
using $9$ different CAD models and a total of \scream{} different
viewpoints, using $X$ different evelation angles, $X$ azimuth angles,
and $X$ focal lengths. We run the entire ensemble exhaustively over
each test image, in a sliding window fashion.

 Performance is measured in Average Precision
(AP) for object detection and Mean Precision in Pose Estimation
(MPPE)~\cite{Lopez-Sastre11}. Pose estimation is here understood as a
discrete problem in which the predicted azimuth angle is binned into a
set of $8$ discrete viewpoint classes.
% Instance-level 2D-3D matching (registration) is a difficult problem
% since we need a CAD model that looks similar to the object in the
% image. Especially, due to extreme intraclass variability of chair
% \cite{Aubry14} used a very large collection of CAD models to cover
% variety of chairs. Similarly, \cite{Lim14}

\paragraph{Results.}
Tab.~\ref{tab:3dobject} gives the corresponding results, comparing our
method to two recent state-of-the-art baselines, the aspect layout
model (ALM~\cite{Xiang12}), and the
DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives corresponding
qualitative results.

We observe that our model performs on par with the state-of-the-art
methods in terms of AP ($99.8$) for cars. It performs slightly worse
on bicycles than DPM-VOC+VP ($93.0$ vs. $98.8$), but on par with the
ALM ($93.0$). In viewpoint estimation, our model performs slightly
worse than both methods ($91.7$ vs. $93.4$ and $97.5$ for cars, and
$87.4$ vs. $91.4$ and $97.5$ for bicycles, respectively).

This result is encouraging, since our approach reaches a level of
performance that is on par to current state-of-the-art while at the
same time being much faster to train. It takes merely a few minutes to
train, while both ALM~\cite{Xiang12} and DPM-VOC+VP~\cite{Pepik12} are
complex models that optimize non-convex objective functions during
training, which is only made tractable by resorting to delayed
constraint generation in the form of hard negative mining, and can
easily take a day on a single machine. In addition, our approach uses
only rendered images, avoiding the need for real-world training data
with costly bounding box and viewpoint annotations.
%
\begin{table}[!htbp]
    \footnotesize
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category. Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
  \label{tab:3dobject}
\end{table}

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D Object Classes~\cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
  \label{fig:3dobject}
\end{figure}

@@

\subsection{Enriching Existing Detections}
%\subsection{Fine-Tuning and Viewpoint Estimation}
\label{sec:exp_enrich}
High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
